---
title: "GWAS with GAPIT"
description: "Run GWAS with GAPIT"
output: rmarkdown::html_vignette
---

```{r setup, include = FALSE}
knitr::opts_chunk$set( eval = F, message = F, warning = F)
```

```{r echo = F}
library(gwaspr)
```

Before the `gwaspr` package can be used, we first need to run GWAS with `GAPIT`.

```{r}
# Load our genotype file in hapmap format
myG <- read.csv("myG_hmp.csv", header = F)
# Load our phenotype file
myY <- read.csv("myY.csv")
# Load our covariate file
myCV <- read.csv("myCV.csv")
```

# Genotype data (myG)

Our population, the LDP, was genotyped using an *exome caputure array* and filtered with the following criteria to yield a data set of 336,367 SNPs, stored in our object `myG`.

- Only Bi-allelic           =  TRUE
- Minimum Read Depth        =  3
- Minor Allele Frequency    = >5%
- Maximum Missing Frequency =  25%
- Heterozygous              = <25%

```{r}
# Map + marker Info
myG[1:10,1:11]
# genotrype calls
myG[1:10,12:17]
```

```{r}
DT::datatable(myG[1:20,1:20])
```

# Phenotype data (myY)

```{r}
DT::datatable(myY)
```

# Covariate data (myCV)

```{r}
DT::datatable(myCV)
```

---

# Run GWAS

Run GWAS on the 3 traits `myY`

```{r eval = F}
library(GAPIT)
```

```{r eval = F}
# Run GWAS
myGAPIT <- GAPIT( Y = myY,
                  G = myG, 
                  PCA.total = 4,
                  model = c("GLM","MLM","MLMM","FarmCPU","BLINK"),
                  Random.model = F, Phenotype.View = F
                )
```

---

# GWAS with Covariate

Run GWAS on the `DTF_Sask_2017` trait with `b` as a covariate.

```{r eval = F}
# Prep data
myY2 <- myY[,c("Name","DTF_Sask_2017")]
colnames(myY2)[2] <- "DTF_Sask_2017_b"
# Run GWAS with a covariate
myGAPIT <- GAPIT( Y = myY2,
                  G = myG, 
                  CV = myCV,
                  PCA.total = 0,
                  model = c("GLM","MLM","MLMM","FarmCPU","BLINK"),
                  Random.model = F, Phenotype.View = F
                )
```

```{r eval = F, echo = F}
# Run GWAS
myGAPIT <- GAPIT( Y = myY[,c(1,4)],
                  G = myG, 
                  PCA.total = 4,
                  model = c("BLINK"),
                  Random.model = F, Phenotype.View = F
                )
```
