---
title: "Summary Tables"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(message = F, warning = F)
```

```{r}
library(gwaspr)
```

# table_GWAS_Results()

The function `table_GWAS_Results()` creates a table of GWAS results. 

Specifying a `folder` is all that is required to produce a GWAS results table.

```{r eval = F}
myResults <- table_GWAS_Results(
  # Specify a folder with GWAS results
  folder = "GWAS_Results/" )
```

Customization

```{r eval = F}
myResults <- table_GWAS_Results(
  # Specify a folder with GWAS results
  folder = "GWAS_Results/",
  # Set threshold level
  threshold = 6.7, 
  # Set suggestive threshold level
  sug.threshold = 5 )
# Save
write.csv(myResults, "GWAS_Results_Table.csv", row.names = F)
```

```{r eval = T}
read.csv("GWAS_Results_Table.csv")[1:20,]
```

---

# table_GWAS_Results_Summary()

The function `table_GWAS_Results_Summary()` creates a summary table of GWAS results. 

Specifying a `folder` is all that is required to produce a GWAS summary results table.

```{r eval = F}
mySummary <- table_GWAS_Results_Summary(
  # Load table_GWAS_Results() object 
  xx = myResults )
```

Customization

```{r eval = F}
mySummary <- table_GWAS_Results_Summary(
  # Load table_GWAS_Results() object 
  xx = myResults, 
  # Should markers be binned
  binMarkers = T, 
  # Set the size of the bin
  binSize = 5000000 )
# Save
write.csv(mySummary, "GWAS_Results_Summary_Table.csv", row.names = F)
```

```{r eval = T}
read.csv("GWAS_Results_Summary_Table.csv")[1:20,]
```
